Manuscript_Github_Pchabaudi_calculateTPM

### 2021-03-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_calculateTPM.Rmd
Saving TPM files
Reading in the TPM to the figure file

knitr::opts_knit$set(root.dir = 
                       "/Users/littlet/Dropbox (The Francis Crick)/Data/Manuscript_pirAnalysis_Github/Pchabaudi24h")
#Note that the above doesn't give an error if the dir doesn't exist

@@

>>>>

knitr::opts_knit$set(root.dir = 
                       ".")
#Note that the above doesn't give an error if the dir doesn't exist

@@

write_csv(twentyfour_rMT,
          file = 'Pchabaudi_TPM_allBioReps.csv')
write_csv(twentyfour_rMT_avg,
          file = 'Pchabaudi_TPM_average.csv')
